---
title: "R Notebook"
output: html_notebook
---

Q1. Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.
```{r}
library(tidyverse)
tweets <- read_csv("4_homework/data/code_clan_tweets.csv")

```


```{r}
ncol(tweets)
nrow(tweets)
colnames(tweets)
```

Q2. Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
tweets %>% 
  filter(is_quote == FALSE) %>% 
  summarise(sum(favorite_count))

```

Q3. Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.
```{r}
tweets %>% 
  filter(is_quote == FALSE) %>% 
  group_by(source) %>% 
  summarise(avg_retweets = mean(retweet_count)) #%>% 
  #format(avg_tweets, digits = 3)
```

Q4. Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
tweets %>%
  mutate(media_type = replace_na(media_type, "text")) %>% 
  group_by(media_type) %>% 
  summarise(total_likes = sum(favorite_count))
  

```

Q5. Find the mean number of characters that a CodeClan tweet contains.
```{r}
tweets %>% 
  summarise(mean(display_text_width))

```

Q6. The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
info <- read_csv("4_homework/data/code_clan_info.csv")
```

```{r}
code_clan_tibble <- 
inner_join(tweets, info, by = "tweet_id")
 
```

Q7. From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.

```{r}
code_clan_tibble %>% 
  mutate(tweet_id = str_to_lower(tweet_id)) %>% 
  mutate(hashtags = str_to_lower(hashtags)) %>% 
  select(tweet_id, hashtags) %>% 
  drop_na()

```

Q8. Some tweets have more than one hashtag, denoted by the c( symbols at the start of the string. Use the str_sub() and str_detect() functions and your codeclan_hashtags tibble from above to find all the cases in which the hashtag string begins with characters.

```{r}
pattern <- "[-#@]"
code_clan_tibble %>% 
  mutate()
```

Q9. Use the str_detect() function to find all tweets with text that mentions “Edinburgh”, and count how many such tweets there are.

```{r}
pattern <- "[Ee][Dd][Ii][Nn][Bb][Uu][Rr][Gg][Hh]"

code_clan_tibble %>% 
  mutate(edinburgh_detected = str_detect(text, pattern)) %>% 
  select(text, edinburgh_detected)
  

```

Q10. Use str_extract_all() with a regular expression to find out which Twitter users CodeClan have been tweeting.

```{r}

```





