---
title: "NHS Borders Cancer Incidence Report"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(fable)
library(tsibble)
library(feasts)
library(tsibbledata)
library(lubridate)

cancer_data <- read_csv("data/opendata_inc9418_hb.csv")
health_boards <- read_csv("data/geography_codes_and_labels_hb2014_01042019.csv")
cancer_data_hb <- left_join(cancer_data, health_boards, "HB") %>% 
  select(Year, HBName, CancerSite, Sex, IncidencesAllAges, EASR)

scotland_data_easr <- cancer_data_hb %>% 
  filter(CancerSite == "All cancer types") %>% 
  filter(Sex == "All") %>% 
  group_by(Year) %>% 
  summarise(median_EASR = median(EASR))
```

<font size="4">
This report details a number of insights into the trends of
cancer incidence in the NHS Borders health board area.</font> 


### Overview of Cancer Trends in Scotland
<br>
```{r, warning=FALSE, message=FALSE}
cancer_data_hb %>% 
  filter(CancerSite == "All cancer types") %>% 
  filter(Sex == "All") %>% 
  group_by(Year) %>% 
  summarise(total_incidence = sum(IncidencesAllAges)) %>% 
  ggplot(aes(x = Year, y = total_incidence/1000)) +
  geom_line() +
  scale_x_continuous(n.breaks = 14) +
  scale_y_continuous(n.breaks = 10) +
  scale_fill_brewer(palette = 1) +
  labs(y = "Total Incidence (k)",
       title = "Cancer Incidence Trend for Scotland") +
  theme(plot.title = element_text(hjust = 0.5, vjust = 1, size=16),
        panel.grid.major.y = element_blank(),
        axis.text.y = element_text(hjust=1.5,size=10),
        axis.title.y = element_text(vjust = 2.5),
        axis.title.x = element_text(vjust = -1),
        plot.background = element_rect(fill = "white", colour = "grey"),
        panel.background = element_rect(fill = "white", colour = "grey"))
```

<font size="4">
* Incidence of all cancers has grown steadily for the past 25 years  
* 5.4% increase since 2014  
* Age standardised rates are more representative of population/age profiles
</font>
<br>
<br>
<br>
<br>

### Cancer Trends in NHS Borders
<br>
```{r, warning=FALSE, message=FALSE}
borders_overview <- cancer_data_hb %>% 
  filter(CancerSite == "All cancer types") %>% 
  filter(HBName =="NHS Borders") %>% 
  filter(Sex == "All") 

  ggplot() +
  geom_line(data = scotland_data_easr, aes(x = Year, y = median_EASR, colour = "Scotland(Median)")) +
  geom_line(data = borders_overview, aes(x = Year, y = EASR, colour = "NHS Borders")) +
  scale_x_continuous(n.breaks = 14) +
  labs(y = "European Age Standardised Rate (per 100,000 person years)",
       title = "Cancer European Age Standardised Rate \nfor NHS Borders/Scotland(Median)")+
  theme(plot.title = element_text(hjust = 0.5, vjust = 1, size=16),
        panel.grid.major.y = element_blank(),
        axis.text.y = element_text(hjust=1.5,size=10),
        axis.title.y = element_text(vjust = 2.5),
        axis.title.x = element_text(vjust = -1),
        plot.background = element_rect(fill = "white", colour = "grey"),
        panel.background = element_rect(fill = "white", colour = "grey"),
        legend.title =element_blank()) +
    scale_colour_brewer(palette = "Set2")
```
<font size="4">  
* Trend for NHS borders rate has followed the Scottish median however has been<br>
higher at many points over the last few years.<br>  
* Population profile for Borders area</font>
<br>
<br>
<br>

### Cancer Types (by Gender)
<br>
```{r, warning=FALSE, message=FALSE}
cancer_data_hb %>% 
  filter(Sex == "Male") %>% 
  filter(CancerSite != "All cancer types") %>% 
  filter(HBName == "NHS Borders") %>% 
  filter(Year >= 2014) %>% 
  group_by(Year) %>% 
  slice_max(order_by = IncidencesAllAges, n = 5) %>% 
  ggplot(aes(x = Year, y = IncidencesAllAges, fill = CancerSite)) +
  geom_col(position = "dodge") +
  scale_fill_brewer(palette = "Set3") +
  labs(y = "Total Incidences",
       title = "Highest Incidence by Cancer Type (Male)") +
  theme(legend.title = element_blank(),
        plot.background = element_rect(fill = "white", colour = "grey"),
        panel.background = element_rect(fill = "white", colour = "grey"))
```
<br>
<font size="4">  
* Cancer types with highest incidence for men<br>
* Consistently been 6 major types, with non-melanoma skin cancer highest 
incidence</font>  
<br>
<br>
```{r, warning=FALSE, message=FALSE}
cancer_data_hb %>% 
  filter(Sex == "Female") %>% 
  filter(CancerSite != "All cancer types") %>% 
  filter(HBName == "NHS Borders") %>% 
  filter(Year >= 2014) %>% 
  group_by(Year) %>% 
  slice_max(order_by = IncidencesAllAges, n = 5) %>% 
  ggplot(aes(x = Year, y = IncidencesAllAges, fill = CancerSite)) +
  geom_col(position = "dodge") +
  scale_fill_brewer(palette = "Set3") +
  labs(y = "Total Incidences",
       title = "Highest Incidence by Cancer Type (Female)") +
  theme(legend.title = element_blank(),
        plot.background = element_rect(fill = "white", colour = "grey"),
        panel.background = element_rect(fill = "white", colour = "grey"))
```
<br>
<font size="4">  
* Highest incidence cancer types have also been consistent in women  
* Non-melanoma skin cancer and breast cancer</font>
<br>
<br>

### Cancer Incidence (Top 5 Cancer Sites)
<br>
```{r, warning=FALSE, message=FALSE}
top_sites <- c("Basil cell carcinoma of the skin",
               "Breast",
               "Carcinoma in situ of the cervix uteri",
               "Colorectal cancer",
               "Non-melanoma skin cancer",
               "Trachea, bronchus and lung",
               "Squamous cell carcinoma of the skin",
               "Prostate")

cancer_data_hb %>% 
  filter(Sex != "All") %>% 
  filter(CancerSite %in% top_sites) %>% 
  filter(HBName == "NHS Borders") %>%
  group_by(Year) %>% 
  summarise(total_incidence = sum(IncidencesAllAges)) %>% 
  ggplot(aes(x = Year, y = total_incidence)) +
  geom_line() +
  scale_x_continuous(n.breaks = 14) +
  labs(y = "Total Incidences",
       title = "Total Cancer Incidence by Top 5 Cancer Types ") +
  theme(legend.title = element_blank(),
        plot.background = element_rect(fill = "white", colour = "grey"),
        panel.background = element_rect(fill = "white", colour = "grey"))
```
<br>
<font size="4">  
* Ideally, forecasting model would be used to predict incidence increase over
next five years  
* Due to time pressure, this was not carried out  
* Overall incidence has shown upward trend over last few years  
* Estimated mean value of last 5 years = 3% increase  
* Planned available resources should take this increase into account for next 
year, including a margin of error</font>
<br>
<br>  

### Possible Further Work   
<font size="4">
* Increased domain knowledge would assist with grouping on cancer type  
* Review of NHS Borders waiting times for cancer treatment  
* Further exploration of any data on cancer survival because this could affect
resource allocation</font>


