---
title: "R Notebook"
output: html_notebook
---

Building explanatory model

```{r}
library(tidyverse)
library(modelr)
library(GGally)
library(lubridate)
```

```{r}
avocados <- read_csv("data/avocado.csv")
```

```{r}
avocados
```
```{r}
avocados %>% 
  distinct(region)
```

```{r}
avocados_tidy <- avocados %>% 
  mutate(month = month(Date))
  
```


```{r}
avocados_tidy <- avocados_tidy %>% 
  mutate(season = case_when(between(month, 3, 5) ~ "Spring",
                            between(month, 6, 8) ~ "Summer",
                            between(month, 9, 11) ~ "Fall",
                            between(month, 1, 2) ~ "Winter",
                            TRUE ~ "Winter"
                            )
         )
```

Not sure whether to do this or not........
```{r}
avocados_test <- avocados_tidy %>% 
  pivot_longer(cols = c("plu_4046", "plu_4225", "plu_4770"), names_to = "variety", values_to = "qty_avocados_sold")

avocados_test <- avocados_test %>% 
   mutate(type = as_factor(type)) %>% 
  mutate(season = as_factor(season))
```


```{r}
avocados_tidy <- avocados_tidy %>% 
  select(-c(X1, Date, year, month, "Total Bags", "Total Volume", region))
```

```{r}
avocados_tidy <- avocados_tidy %>% 
  mutate(type = as_factor(type)) %>% 
  mutate(season = as_factor(season))
```

```{r}
avocados_tidy <- avocados_tidy %>% 
  rename(plu_4046 = "4046",
         plu_4225 = "4225",
         plu_4770 = "4770")
```

First model

```{r}
avocados_tidy %>% 
  ggpairs() %>% 
  ggsave(filename = "ggpairs", device = "jpeg")
```

From ggpairs output, type and 4046 look like most promising predictors
```{r}
mod1a <- lm(AveragePrice ~ plu_4046, data = avocados_tidy)
summary(mod1a)
```

R squared is very low (0.0434) so now trying type as predictor
```{r}
mod1b <- lm(AveragePrice ~ type, data = avocados_tidy)
mod1b
```

```{r}
summary(mod1b)
```

```{r}
par(mfrow = c(2,2))
plot(mod1b)
```
These plots look ok for categorical type so moving on to second predictor

```{r}
avocados_rem_residuals <- avocados_tidy %>% 
  add_residuals(mod1b) %>% 
  select(-c("AveragePrice", "type"))
```

```{r}
avocados_rem_residuals %>% 
  ggpairs() %>% 
  ggsave(filename = "ggpairs_2nd", device = "jpeg")
```

Second predictor - looks like season is the only thing that may have some affect
```{r}
mod2a <- lm(AveragePrice ~ type + season, data = avocados_tidy)
summary(mod2a)
```

```{r}
par(mfrow = c(2,2))
plot(mod2a)
```
Again all these plots look reasonable, but the r squared value is still 
relatively low at 0.431 (with mod 2a type + season)

Third predictor
```{r}
avocados_rem_residuals <- avocados_tidy %>% 
  add_residuals(mod2a) %>% 
  select(-c("AveragePrice", "type", "season"))
```

```{r}
avocados_rem_residuals %>% 
  ggpairs() %>% 
  ggsave(filename = "ggpairs_3rd", device = "jpeg")
```

```{r}
mod3a <- lm(AveragePrice ~ type + season + plu_4046, data = avocados_tidy)
summary(mod3a)
```




