---
title: "R Notebook"
output: html_notebook
---

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(modelr)
library(yardstick)
library(caret)
library(randomForest)
library(GGally)
```

```{r}
titanic <- read_csv("data/titanic_decision_tree_data.csv")
```

Question 1
```{r}
titanic_clean <- titanic %>% 
  drop_na(survived, age) %>% 
  mutate(sex = factor(sex),
         survived = factor(if_else(survived == 1, "Survived", "Died")),
         pclass = factor(pclass),
         embarked = factor(embarked),
         age_status = factor(if_else(age > 16, "Adult", "Child"))) %>% 
  select(-c(X1, passenger_id, name, ticket, fare, cabin))
  
```

Question 2
```{r}
titanic_clean %>% 
  ggpairs()
```

From the boxplots above, it looks like pclass, sex and embarked may be variables
of interest.  Age status may also be a factor but hard to tell.

Question 3
```{r}
n_data <- nrow(titanic_clean)
```

```{r}
test_index <- sample(1:n_data, size = n_data * 0.2)
```

```{r}
titanic_test <- slice(titanic_clean, test_index)
titanic_train <- slice(titanic_clean, -test_index)
```

```{r}
titanic_test %>% 
  janitor::tabyl(survived)
```

```{r}
titanic_train %>% 
  janitor::tabyl(survived)
```

This split for both sets is close, so ok to proceed with analysis. The split of
the data is using a random sample of 20% of the row numbers to create the test sample
and the remaining rows are the training sample.

Question 4
```{r}
titanic_fit <- rpart(
  formula = survived ~ .,
  data = titanic_train,
  method = "class"
)
```

```{r}
rpart.plot(titanic_fit, yesno = 2, fallen.leaves = TRUE, faclen = 6, digits = 4,
           type = 4, extra = 101)
```

Question 5

The model tells us that 63.81% of passengers who died were male, versus 36.19 % 
female.
338 people died versus 234 survived.  Of the 234 survivors, 156 were women and 
78 were men.
Of the 338 people who died, 287 were men and 51 were women

For males, if you were older than 13 you were more likely to die. If you were
male, under 13 and had less than 3 siblings aboard you were less likely to die
(19 survived versus 1)

For females, if you were in passenger class 1,2 you had better chance of surviving
versus those in passenger class 3(115 versus 41)

For those in class 3 who were female, if you were younger than 38.5 and had less 
than 3 siblings/spouses you were more likely to survive.

Variables of importance - sex, age, class, number siblings/spouses

Highest chance of survival - female in class 1,2
Lowest chance of survival - male older than 13

Question 6

```{r}
titanic_test_pred <- titanic_test %>% 
  add_predictions(titanic_fit, type = "class")

titanic_test_pred 
```

```{r}
confusion_matrix <- titanic_test_pred %>% 
  conf_mat(truth = survived, estimate = pred)

confusion_matrix
```

Model predicted 75 people died accurately.
Model predicted 42 people survived accurately.

Model incorrectly predicted 14 survived but they actually died.
Model incorrectly predicted 11 died but they actually survived.












