---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(lubridate)
library(tsibble)
library(tsibbledata)
library(fable)
```

Question 1:
```{r}
bike_data <- nyc_bikes %>% 
  mutate(year = year(start_time),
         month = month(start_time, label = TRUE),
         date = as_date(start_time))
```

Question 2:
```{r}
bike_count <- bike_data %>% 
  select(month) %>% 
  index_by(month) %>% 
  summarise(no_bikes = n())

bike_count %>% 
  ggplot(aes(x = month, y = no_bikes)) +
  geom_point() +
  geom_line(group = 1)
```
This would tell you there will likely be an increase in demand during the summer, but not about daily variation so you may need a finer level of granularity.

Question 3:
```{r}
bike_count_date <- bike_data %>% 
  select(date) %>% 
  index_by(date) %>% 
  summarise(no_bikes = n())

bike_count_date %>% 
  ggplot(aes(x = date, y = no_bikes)) +
  geom_point() +
  geom_line(group = 1)
```
This would be more helpful as it would tell you if particular days (eg weekends) are busier or public holidays are busier.

Question 4:
```{r}
library(urca)

padded_bike_count_date <- bike_count_date %>% 
  fill_gaps(no_bikes = as.integer(median(no_bikes)))

  
  fit <- padded_bike_count_date %>% 
  model(
    snaive = SNAIVE(no_bikes),
    mean_model = MEAN(no_bikes),
    naive = NAIVE(no_bikes)
  )
fit
```

Question 5:
```{r}
forecast_1 <- fit %>% 
  fabletools::forecast(h = 120)

forecast_1 %>% 
  autoplot(padded_bike_count_date, level = NULL) +
  ggtitle("Forecast for NYC Bikes") +
  xlab("Date") +
  guides(colour = guide_legend(title = "Forecast"))
```

Question 6: First six months of year
```{r}
training <- padded_bike_count_date %>% 
  filter_index("2018-01-01" ~ "2018-10-30")

fit_training <- training %>% 
  model(
    mean_model = MEAN(no_bikes),
    naive = NAIVE(no_bikes),
    snaive = SNAIVE(no_bikes)
  )
```

```{r}
forecast_test <- fit_training %>%
  fabletools::forecast(h = 180)
forecast_test %>%
  autoplot(training, level = NULL) +
  autolayer(padded_bike_count_date, colour = "black") +
  ggtitle("Forecasts for NYC Bike Use") +
  xlab("Date") +
  ylab("No. of Bikes") +
  guides(colour = guide_legend(title = "Forecast"))
```

Accuracy
```{r}
accuracy_model <- fabletools::accuracy(forecast_test, padded_bike_count_date)

accuracy_model
```

Question 7:
Both the forecast plots and accuracy do not seem very accurate.  It appears the model does not recognise the seasonal effects of bike use and is prediciting a downward trend, even although it appeasrs there should be steady use of bikes at the lower level during Jan - April, with an increase after that.  I think it would help to have data from a couple of years so that the seasonal affects can be recognised by the models.  Also, if it were possible to use a model that better accounted for seasonal affects, that should perhaps be used and assessed. 

Question 8:
```{r}
bike_data %>% 
  ggplot(aes(x = start_long, y = start_lat, colour = month)) +
  geom_point() +
  facet_wrap(~ bike_id, ncol = 5)
```

```{r}
bike_data %>% 
  ggplot(aes(x = end_long, y = end_lat, colour = month)) +
  geom_point() +
  facet_wrap(~ bike_id, ncol = 5)
```
Some bikes mainly used in summer months and some only used in winter months.

Question 9:
```{r}
library(leaflet)
leaflet(bike_data) %>% 
  addTiles() %>% 
  addCircleMarkers(
    lng = ~start_long, 
    lat = ~start_lat, 
    radius = ~ 5,
    weight = 1)
```









