---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
```

Question 1:
```{r}
colnames(backpack)
glimpse(backpack)
```

Question 2 - What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.
```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_histogram(col = "white") +
  labs(y = "No. of Students",
       x = "Backpack Weight")
```


Question 3 - Are there differences in backpack weight between sex?
```{r}
ggplot(backpack) +
  aes(x = backpack_weight, fill = sex) +
  geom_histogram(col = "white") +
  labs(y = "No. of Students",
       x = "Backpack Weight") +
  facet_wrap(~ sex, ncol = 1)
```
As can be seen from above charts, there is no great difference in the distribution of backpack weights when comparing male versus female.

Question 4 - What is the relationship between body weight and backpack weight?
```{r}
ggplot(backpack) +
  aes(x = body_weight, y = backpack_weight) +
  geom_point(position = "jitter") +
  labs(
    x = "Body Weight",
    y = "Backpack Weight",
    title = "Body Weight versus Backpack Weight"
  )
```
A weak positive relationship with body weight and backpack weight.

Question 5 - Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
ggplot(backpack) +
  aes(x = body_weight, y = backpack_weight, colour = sex) +
  geom_point(position = "jitter") +
  labs(
    x = "Body Weight",
    y = "Backpack Weight",
    title = "Body Weight versus Backpack Weight"
  )+ facet_wrap( ~ sex, ncol = 1)
```
Strength of relationship looks slightly more positive for women.  There is also a difference in the range of bodyweights in women versus men (women have more data points in the lighter bodyweight range).

Question 6 - What proportion of students report back pain?
```{r}
library(scales)

ggplot(backpain, aes(x = factor(back_problems))) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels = percent) +
  labs(y = "% Students",
       x = "Reported Back Problems")
```

Question 7 - Is this proportion different between men and women?
```{r}
ggplot(backpain, aes(x = factor(back_problems)), position = "fill") +
  geom_bar(aes(y = (..count..)/sum(..count..), fill = sex)) +
  scale_y_continuous(labels = percent) +
  labs(y = "% Students",
       x = "Reported Back Problems")
```

Question 8 - Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

```{r}
ggplot(backpack, aes(x = factor(back_problems)), position = "fill") +
  geom_bar(aes(y = (..count..)/sum(..count..), fill = sex)) +
  scale_y_continuous(labels = percent) +
  labs(y = "% Students",
       x = "Reported Back Problems") +
  facet_grid(~ body_weight, back_problems)
```










