---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
```

```{r}
data(msleep)
```

Determine whether the mean sleep_total in sampled population of animal types differs from jabberwockies (7 hours on average)

alpha = 0.05
H0: Sample animals sleep_total = jabberwockies
Ha: Sample animals sleep_total != jabberwockies

```{r}
msleep %>% 
  ggplot(aes(x = sleep_total)) +
  geom_histogram(bins = 50)
```
```{r}
observed_stat <- msleep %>% 
  summarise(mean_sleep = mean(sleep_total))

observed_stat
```

```{r}
null_distribution <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 10.434) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")

null_distribution
```
```{r}
null_distribution %>% 
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat$mean_sleep, direction = "both")
```

```{r}
p_value <- null_distribution %>% 
  get_p_value(obs_stat = observed_stat$mean_sleep, direction = "both")
p_value
```

p_value is greater than alpha, fail to reject null hypothesis so cannot say that mean sleep_total of sample differs significantly from jabberwockies.
----------------------------------------------------------------------------

Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

alpha = 0.05
H0: omnivores sleep_total = herbivores sleep_total
Ha: omnivores sleep_total > herbivores sleep_total

```{r}
vore_comparison <- msleep %>%
  filter(vore == "omni" |
         vore == "herbi")

vore_comparison %>% 
  ggplot(aes(y = sleep_total, x = vore)) +
  geom_boxplot()

```

```{r}
null_distribution <- vore_comparison %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 10000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))
null_distribution
```
```{r}
observed_stat <- vore_comparison %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

observed_stat
```

```{r}
null_distribution %>% 
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction = "right")
```

```{r}
null_distribution %>% 
  get_p_value(obs_stat = observed_stat, direction = "right")
```

p value > alpha, therefore fail to reject null hypothesis so cannot say for certain that omnivores sleep more than herbivores on average.
---------------------------------------------------------------------------
Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.
[Hint - think about creating an is_domesticated variable for the analysis]

```{r}
domesticates <- msleep %>% 
  mutate(is_domesticated = ifelse(conservation == "domesticated", "domesticated", "not domesticated")) %>% 
  mutate(is_domesticated = ifelse(is.na(conservation) == TRUE, "not domesticated", is_domesticated))
```

```{r}
prop_domesticated <- domesticates %>% 
  group_by(is_domesticated) %>% 
  summarise(prop = n() / nrow(domesticates)) %>% 
  filter(is_domesticated == "domesticated")
```
alpha = 0.05
H0:prop_domesticated = 0.05
ha:prop_domesticated > 0.05

```{r}
null_distribution <- domesticates %>% 
  specify(response = is_domesticated, success = "domesticated") %>% 
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 5000, type = "simulate") %>% 
  calculate(stat = "prop")
```

```{r}
null_distribution %>% 
  visualise(bins = 10)
```

```{r}
observed_stat <- domesticates %>% 
  specify(response = is_domesticated, success = "domesticated") %>% 
  calculate(stat = "prop")

observed_stat
```

```{r}
null_distribution %>% 
  get_p_value(obs_stat = observed_stat, direction = "right")
```

p value < alpha, therefore reject H0 and it can be said that the proportion of domesticated animals > 0.05.


Hypothesis Testing - Interpretation
===================================
1. H0: pi_before_marketing = pi_after_marketing
   Ha: pi_after_marketing > pi_before_marketing
   
   H0: % Customer awareness of coffee store after marketing campaign = 40%
   Ha: % Customer awareness of coffee store after marketing campaign > 40%
   
   Method = permutation
   
2. H0: pi_CTR_group1 = pi_CTR_test_group
   Ha: pi_CTR_test_group > pi_CTR_group1
   
   H0: % click through rate in group 1(no changes to page) is the same as 
       % click through rate in test group(banner moved to top)
   Ha: % click through rate in group 1(no changes to page) is not the same        as % click through rate in test group(banner moved to top)
   
   Method = permutation

3. H0: mu_mean_width = 145mm
   Ha: mu_mean_width != 145mm
   
   H0: the mean width of the sample parts is equal to 145 mm
   Ha: the mean width of the sample parts is not equal to 145 mm
   
   Method = bootstrap
   
Interpreting the Results
==========================
1. p value greater than alpha, therefore fail to reject null hypothesis therefore it can be said that there is no statistically significant increase in the % awareness of the coffee shop after marketing campaign.

2. p value less than alpha, reject null hypothesis.  It can be said that the test group had a statistically significantly higher click through rate than group 1, therefore banner position made a statistically significant increase to click through rate.

3. p value  greater than alpha, therefore fail to reject null hypothesis.  It can be said that it is statistically likely that the mean width of population parts is 145mm.







