---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
```

```{r}
data(msleep)
```

Determine whether the mean sleep_total in sampled population of animal types differs from jabberwockies (7 hours on average)

alpha = 0.05
H0: Sample animals sleep_total = 7
Ha: Sample animals sleep_total != 7

```{r}
msleep %>% 
  ggplot(aes(x = sleep_total)) +
  geom_histogram(bins = 50)
```


```{r}
null_distribution <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "mean")

null_distribution
```

```{r}
obs_stat <- msleep %>%
  specify(response = sleep_total) %>%
  calculate(stat = "mean")
```




```{r}
null_distribution %>% 
  visualise(bins = 30) +
  shade_p_value(obs_stat = obs_stat, direction = "both")
```

```{r}
p_value <- null_distribution %>% 
  get_p_value(obs_stat = obs_stat, direction = "both")
p_value
```

p_value is less than alpha,  reject null hypothesis so can say that mean sleep_total of sample differs significantly from jabberwockies ttal of 7.
----------------------------------------------------------------------------

Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

alpha = 0.05
H0: omnivores sleep_total = herbivores sleep_total
Ha: omnivores sleep_total > herbivores sleep_total

```{r}
vore_comparison <- msleep %>%
  filter(vore == "omni" |
         vore == "herbi")

vore_comparison %>% 
  ggplot(aes(y = sleep_total, x = vore)) +
  geom_boxplot()

```

```{r}
null_distribution <- vore_comparison %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 10000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))
null_distribution
```
```{r}
observed_stat <- vore_comparison %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

observed_stat
```

```{r}
null_distribution %>% 
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction = "right")
```

```{r}
null_distribution %>% 
  get_p_value(obs_stat = observed_stat, direction = "right")
```

p value > alpha, therefore fail to reject null hypothesis so cannot say for certain that omnivores sleep more than herbivores on average.
---------------------------------------------------------------------------
Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.
[Hint - think about creating an is_domesticated variable for the analysis]

```{r}
domesticates <- msleep %>% 
  mutate(is_domesticated = ifelse(conservation == "domesticated", "domesticated", "not domesticated")) %>% 
  mutate(is_domesticated = ifelse(is.na(conservation) == TRUE, "not domesticated", is_domesticated))
```

```{r}
prop_domesticated <- domesticates %>% 
  group_by(is_domesticated) %>% 
  summarise(prop = n() / nrow(domesticates)) %>% 
  filter(is_domesticated == "domesticated")
```
alpha = 0.05
H0:prop_domesticated = 0.05
ha:prop_domesticated > 0.05

```{r}
null_distribution <- domesticates %>% 
  specify(response = is_domesticated, success = "domesticated") %>% 
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 5000, type = "simulate") %>% 
  calculate(stat = "prop")
```

```{r}
null_distribution %>% 
  visualise(bins = 10)
```

```{r}
observed_stat <- domesticates %>% 
  specify(response = is_domesticated, success = "domesticated") %>% 
  calculate(stat = "prop")

observed_stat
```

```{r}
null_distribution %>% 
  get_p_value(obs_stat = observed_stat, direction = "right")
```

p value < alpha, therefore reject H0 and it can be said that the proportion of domesticated animals > 0.05.


Hypothesis Testing - Interpretation
===================================

1. One-sample proportion, right-sided.
   H0: pi_before_marketing = pi_after_marketing
   Ha: pi_after_marketing > pi_before_marketing
   
   H0: % Customer awareness of coffee store after marketing campaign = 40%
   Ha: % Customer awareness of coffee store after marketing campaign > 40%
   
   Method = simulation
   
   
2. Two-samples proportion, right-sided.
   H0: pi_CTR_group1 = pi_CTR_test_group
   Ha: pi_CTR_test_group > pi_CTR_group1
   
   H0: % click through rate in group 1(no changes to page) is the same as 
       % click through rate in test group(banner moved to top)
   Ha: % click through rate in group 1(no changes to page) is not the same        as % click through rate in test group(banner moved to top)
   
   Method = permutation

3. One-sample mean test, two-sided.
   H0: mu_mean_width = 145mm
   Ha: mu_mean_width != 145mm
   
   H0: the mean width of the sample parts is equal to 145 mm
   Ha: the mean width of the sample parts is not equal to 145 mm
   
   Method = bootstrap
   
Interpreting the Results
==========================
1. p value greater than alpha, therefore fail to reject null hypothesis therefore it can be said that there is not enough evidence to say there is a statistically significant increase in the % awareness of the coffee shop after marketing campaign.

2. p value less than alpha, reject null hypothesis.  It can be said that the test group had a statistically significantly higher click through rate than group 1, therefore banner position made a statistically significant increase to click through rate.

3. p value  greater than alpha, therefore fail to reject null hypothesis.  It can be said that there is not enough evidence to say that the mean width of population parts is not 145mm.







