---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(gtools)
library(prob)
library(janitor)

titanic_data <- read_csv("data/titanic.csv")
```

```{r}
titanic_data %>% 
  distinct(class)
```
```{r}
titanic_data <- titanic_data %>% 
  mutate(is_passenger = str_detect(class, "[0-9][a-z]{2}")) %>% 
  select(survived, is_passenger)
```


```{r}
table <- titanic_data %>%
  tabyl(survived, is_passenger)
table <- table %>%
  adorn_totals(where = c("row", "col")) %>%
  adorn_percentages(denominator = "all") %>%
  adorn_title()
table
```

```{r}
n_row_survived <- titanic_data %>% 
  dplyr::filter(survived == "yes") %>% 
  nrow()
n_row_survived
```


prob( survived ∣ crew )

```{r}
prob_survived_crew <- titanic_data %>% 
  dplyr::filter(is_passenger == FALSE) %>% 
  summarise(prob = sum(survived == "yes") / n())

prob_survived_crew
```

prob( survived ∣ passenger )

```{r}
prob_survived_passenger <- titanic_data %>% 
  dplyr::filter(is_passenger == TRUE) %>% 
  summarise(prob = sum(survived == "yes") / n())

prob_survived_passenger
```

2 MVP

1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?
=============================================================================================

no. outcomes = 1,2,3,4 = 4
no possible outcomes = 6
probability = 4/6 = 0.66.

2. How many outcomes are there in the sample space of an experiment in which we toss three dice?
================================================================================================

no.outcomes = 6 * 6 * 6
            = 216
            
3. In an experiment where we roll four dice:

i) how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)?

```{r}
roll_4_dice <- rolldie(4) %>% 
  mutate(sum = X1 + X2 + X3 + X4)

no_outcomes <- roll_4_dice %>% 
  dplyr::filter(sum >= 5 & sum <= 7) %>% 
  nrow()
no_outcomes
```

ii) what is the probability of this event?

```{r}
prob_tot_5_6_7 <- no_outcomes / nrow(roll_4_dice)
prob_tot_5_6_7
```

iii) what assumptions do we apply in answering part ii?
All outcomes equally likely e.eg rolling 1,2,3,4,5,or 6

4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?
==================================================================================================

```{r}
folk <- c("Shortest Jim", "Slightly taller Bob", "Average height Claire", "Taller than average Joe", "Tallest Sally")

height_order <- as_tibble(permutations(n = 5, r = 5, v = folk, repeats.allowed = FALSE))

height_order <- height_order %>% 
  rename(chair_1 = V1,
         chair_2 = V2,
         chair_3 = V3,
         chair_4 = V4,
         chair_5 = V5)
nrow(height_order)
```

```{r}
height_order %>% 
  dplyr::filter(chair_1 == "Tallest Sally",
               chair_2 == "Taller than average Joe",
               chair_3 == "Average height Claire",
               chair_4 =="Slightly taller Bob",
               chair_5 == "Shortest Jim") %>% 
  summarise(prob = n() / nrow(height_order))

```

5. I roll six dice:
what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
=================================================================================================
```{r}
dice_6 <- rolldie(6)
dice_6

dice_6 %>% 
  dplyr::filter(X1 == 6,
                X2 == 5,
                X3 == 4,
                X4 == 3,
                X5 == 2,
                X6 == 1) %>% 
  summarise(n() / nrow(dice_6))

```

what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
=================================================================================================

???


Q6. If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

```{r}
cards <- cards(jokers = FALSE) %>% 
 mutate(card = str_c(rank, str_sub(suit, start = 1, end = 1))) 

cards_black_prob <- cards %>% 
  mutate(black_card = str_detect(card, "C") | str_detect(card, "S")) %>% 
  dplyr::filter(black_card == TRUE) %>% 
  summarise(prob = n() / nrow(cards))
cards_black_prob

```




