---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
library(janitor)
```

```{r}
ames_data <- read_csv("data/ames.csv") %>% 
  clean_names() %>% 
  select(lot_area)
```

```{r}
ames_data %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram(col = "white", bins = 100)
```
The data has part of a normal bell curve, but the range of values is very large so there is a long tail but it cannot be seen on the chart because the count is very small compared with smaller lot areas.

Bootstrap Sample
```{r}
bootstrap_sample <- ames_data %>% 
  specify(response = lot_area) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

```{r}
bootstrap_sample %>% 
 ggplot(aes(x = stat)) +
  geom_histogram(col = "white", bins = 20)
```

```{r}
ci_95 <- bootstrap_sample %>% 
  get_ci(level = 0.95, type = "percentile")
ci_95 
```

```{r}
bootstrap_sample %>% 
  visualise() +
  shade_ci(endpoints = ci_95)
```

```{r}
ci_99 <- bootstrap_sample %>% 
  get_ci(level = 0.99, type = "percentile")
ci_99
```

```{r}
bootstrap_sample %>% 
  visualise() +
  shade_ci(endpoints = ci_99)
```

The range is broader, which makes sense as the confidence interval has increased.

Point estimate
```{r}
ames_data %>%
  summarise(
    mean_lot_area = mean(lot_area)
  )
```

Extension
```{r}
old_houses <- read_csv("data/ames.csv") %>% 
  clean_names() %>% 
  select(year_built) %>% 
  mutate(before_1920 = as.numeric(year_built < 1920))
```

```{r}
bootstrap_sample_old_200 <- old_houses %>% 
  specify(response = before_1920) %>% 
  generate(reps = 200, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

```{r}
ci_95 <- bootstrap_sample_old_200 %>% 
  get_ci(level = 0.95, type = "percentile")
ci_95 
```

```{r}
bootstrap_sample_old_200 %>%
  summarise(point_est = mean(stat))
```

```{r}
bootstrap_sample_old_10000 <- old_houses %>% 
  specify(response = before_1920) %>% 
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

```{r}
ci_95_1000 <- bootstrap_sample_old_10000 %>% 
  get_ci(level = 0.95, type = "percentile")
ci_95_1000 
```

```{r}
bootstrap_sample_old_10000 %>%
  summarise(point_est = mean(stat))
```

With increasing reps, the range has increased. However the difference is very slight in this case. 

